\ttitle

### 2015-07-16 Chapters/Introduction.tex
Numerous small formatting changes
- Linespacing set to 1.5
- Several tables placement changed from htbp to p
- Other minor changes
- Email this version to Donny

\subsection{Epidemiology of pancreatic cancer}
\parencite{crozier_preoperative_2007}
Tumours involving the head of the pancreas and the periampullary region account for a small proportion of gastrointestinal tumours. They may be broadly classified as benign and malignant. Most pancreatic neoplasia are malignant and arise from the exocrine component of the gland, the ductal epithelium.

>>>>

\subsection{Epidemiology of pancreatic cancer}
Tumours involving the head of the pancreas and the periampullary region account for a small proportion of gastrointestinal tumours. They may be broadly classified as benign and malignant. Most pancreatic neoplasia are malignant and arise from the exocrine component of the gland, the ductal epithelium.

### 2015-07-16 main.tex
CPET Survival Cox Univariate regression
- Complete CPET vs Survival Univariate table
- Create new SPSS dataset for this chapter -ds_at_pdac
- Remove redundant variables in this dataset
- Changes to main.tex are simply commenting out other chapters from output
Additions to results section of CPET Survival
- Add description of results of Cox regression to CPET Survival
- Shorten cpet_survival_cox_regression table by condensing rows into one per parameter
- Save long form of above table in separate file - not currently in use
- New table - cpet_survival_6months - needs fleshing out
- Add todo to

\usepackage{graphicx}
\usepackage{caption} 
\usepackage{subcaption} % For Subfigures - not sure if I have used this anywhere
\usepackage{parskip} %Adds extra space between paragraphs
\usepackage{listings} %This is for the VBA code in the appendices
\usepackage{amsmath} %For aligning all equations on the equal to sign
\usepackage{pdfpages} %for including pdf files or individual pages of pdf files
\usepackage{easy-todo} %Adds todos to the document. Use [diable] as package option in final verion. Also see \listoftodos below.
\usepackage[pagewise]{lineno} %To help Donny review. Remove for final version
\linenumbers

@@

\setstretch{2.0} % Line spacing of 2.0 although I have set \doublespace set somewhere else

@@

\lhead{\emph{List of Figures}} % Set the left side page header to "List of Figures"
\listoffigures % Write out the List of Figures

\lhead{\emph{List of Tables}} % Set the left side page header to "List of Tables"
\listoftables % Write out the List of Tables

@@

% Include the chapters of the thesis as separate files from the Chapters folder
\input{Chapters/Introduction}
\input{Chapters/CPET_Outcomes} 
\input{Chapters/CPET_Jaundice}
\input{Chapters/BodyComp}
\input{Chapters/CPET_Survival}
\input{Chapters/Discussion}

@@

%\input{Appendices/AppendixExcelMacros}
\input{Appendices/AppendixCPETRawData}
%\input{Appendices/AppendixC}

@@

%\bibliographystyle{unsrtnat} % Use the "unsrtnat" BibTeX style for formatting the Bibliography
\printbibliography % The references (bibliography) information are stored in the file named "Bibliography.bib"

>>>>

\usepackage{graphicx}
\usepackage{caption} 
\usepackage{subcaption} % For Subfigures - not sure if I have used this anywhere
\usepackage{parskip} %Adds extra space between paragraphs
\usepackage{listings} %This is for the VBA code in the appendices
\usepackage{amsmath} %For aligning all equations on the equal to sign
\usepackage{pdfpages} %for including pdf files or individual pages of pdf files
\usepackage{easy-todo} %Adds todos to the document. Use [disable] as package option in final verion. Also see \listoftodos below.
\usepackage[pagewise]{lineno} %To help Donny review. Remove for final version
\linenumbers

@@

\setstretch{1.5} % Line spacing of 1.5 although I have set \doublespace set somewhere else - not sure where

@@

\clearpage
\lhead{\emph{List of Figures}} % Set the left side page header to "List of Figures"
\listoffigures % Write out the List of Figures

\clearpage
\lhead{\emph{List of Tables}} % Set the left side page header to "List of Tables"
\listoftables % Write out the List of Tables

@@

% Include the chapters of the thesis as separate files from the Chapters folder
\input{Chapters/Introduction} 		%1
\input{Chapters/CPET_Outcomes} 	%2
\input{Chapters/CPET_Jaundice} 	%3
\input{Chapters/BodyComp}			%4
\input{Chapters/CPET_Survival}		%5
\input{Chapters/CRP_Complications}	%6
\input{Chapters/Discussion}		%7

@@

\input{Appendices/AppendixExcelMacros}
\input{Appendices/AppendixCPETRawData}
%\input{Appendices/AppendixC}

@@

%\bibliographystyle{unsrtnat} % Use the "unsrtnat" BibTeX style for formatting the Bibliography
\printbibliography
